### 2023-05-20 test_running_updating.Rmd
updated httptest and mock tests

```{r}
library(testthat)
library(roxygen2)
library(devtools)
system("rm -rf tests/api")
roxygen2::roxygenise()
devtools::install(build_vignettes = FALSE)
testthat::test_local(".")
all_mock_dirs <- dir("tests/api", full.names = TRUE, recursive = TRUE) |>
  dirname() |>
  unique()
new_mock_dirs <- gsub(
  "api.aims.gov.au/data-v2.0/10.25845", "a", all_mock_dirs, fixed = TRUE
)
for (i in seq_along(all_mock_dirs)) {
  system(paste0("mkdir -p ", new_mock_dirs[i]))
  system(paste0(
    "cp -R ", all_mock_dirs[i], "/* ", new_mock_dirs[i], "/" , collapse = ""
  ))
  to_rm <- dirname(all_mock_dirs[i]) |>
    dirname() |>
    dirname()
  system(paste0("rm -rf ", to_rm))
}
```

This will delete all existing mock files and regenerate them. Then return to root directory and check if it all passes:

>>>>

```{r}
library(httptest) # installed from https://github.com/nealrichardson/httptest/commit/5fc2be9f8627fa36d04ee06de0291c1d7633d1a8
library(testthat)
library(roxygen2)
library(devtools)
system("rm -rf tests/api")
roxygen2::roxygenise()
devtools::install(build_vignettes = FALSE)
testthat::test_local(".")
```

The above block will delete all existing mock files and regenerate them. Then return to root directory and check if it all passes:
